---
title: "R Project 1 - Hello R"
author: "Chimzurumoke Orji"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 5
    highlight: monochrome
    theme: cosmo
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
```{r}
datasaurus_dozen %>%
count(dataset) %>%
print(13)

```
### Exercise 2

```{r plot-dino, fig.height=6, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3





```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Finishing up the calculations.
 
```{r cor-star}

star_data %>%
  summarize(r = cor(x, y))
##Lower than dinoset

```

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r plot-circle}

circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}

circle_data %>%
  summarize(r = cor(x, y))
##Higher than dinoset
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

```{r fig.height=15, fig.width=15}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
## `summarise()` ungrouping output (override with `.groups` argument)
## # A tibble: 13 x 2
## dataset r
## <chr> <dbl>
## 1 away -0.0641
## 2 bullseye -0.0686
## 3 circle -0.0683
## 4 dino -0.0645
## 5 dots -0.0603
## 6 h_lines -0.0617
## 7 high_lines -0.0685
## 8 slant_down -0.0690
## 9 slant_up -0.0686
## 10 star -0.0630
## 11 v_lines -0.0694
## 12 wide_lines -0.0666
## 13 x_shape -0.0656

```



